`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-02-03 inst/manuscript/manuscript.rmd
Order shuffle;
Minor change in pandoc argument handling by rstudio;

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
    pandoc_args: ["--smart"]
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---

@@

## Funding {-}
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21. No funding body was involved in the design of or conclusions drawn
from this study.

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    pandoc_args: --smart
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---

@@

## Funding {-}
R.J.C., J.G. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21. No funding body was involved in the design of or conclusions drawn
from this study.
